refnx -- Neutron and X-ray reflectometry analysis in Python

### 2018-08-13 paper/manuscript.tex
Add synopsis
tidy caption

\begin{synopsis}
%TODO synopsis for ToC
\end{synopsis}

%TODO en_GB or en_US?

@@

\caption{a) Neutron reflectivity from a DMPC bilayer supported on a silicon crystal, measured at three contrasts, with 500 samples from the posterior distribution in grey and median of the distribution in red. Data for the hdmix and \ce{H_2O} contrast offset by 0.1 and 0.01 respectively. b) SLD profile of the \ce{D_2O} model showing 500 samples from the posterior distribution, as well as the median in red. It is seen that the uncertainty in the reflectivity at high $Q$ is associated with an uncertainty in SLD profile at the lipid-\ce{D2O} interface.}
\end{figure}

>>>>

\begin{synopsis}
The refnx Python modules for neutron and X-ray reflectometry data analysis are
introduced. An sample analysis illustrates a Bayesian approach using a
Markov Chain Monte Carlo algorithm to understand the confidence in the fit parameters.
\end{synopsis}

@@

\caption{a) Neutron reflectivity from a DMPC bilayer supported on a silicon crystal, measured at three contrasts, with 500 samples from the posterior distribution in grey and median of the distribution in red. Data for the contrast matched (HD\textsubscript{mix}) and \ce{H2O} contrast offset by 0.1 and 0.01 respectively. b) SLD profile of the \ce{D2O} model showing 500 samples from the posterior distribution, as well as the median in red. It is seen that the uncertainty in the reflectivity at high $Q$ is associated with an uncertainty in SLD profile at the lipid-\ce{D2O} interface.}
\end{figure}
